Opening Restaurants During COVID-19 Can Prove Beneficial for Restaurant Revenue in the GTA

### 2021-02-27 outputs/Paper.Rmd
update

```{r ttest, echo=FALSE}
#install.packages("broom")
library(broom)
revenue_c <- control_data$Q13
revenue_t <- treated_data$Q13
t<-t.test(revenue_t, revenue_c)
m<-tidy(t, digits=1)
m%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    mean_of_Treated=estimate1,
    mean_of_Control=estimate2
  )%>%
  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()

@@

## Appendix A {#appendixA}
```{r AppendixA, message=FALSE, echo = FALSE}
### Number in GTA ### 
number_of_Toronto = 7500
number_of_Durham = 3260
number_of_York = 5553
number_of_Peel = 6235
number_of_Halton = 2803
number_of_GTA = sum(number_of_Toronto,number_of_Durham,number_of_York,number_of_Peel,number_of_Halton)

@@

### Table ###
library(kableExtra)
sample_size %>% 
  knitr::kable(caption = "Detailed information for stratification",
               col.names = c("Region", "Number of Restuarants", "Proportion(%)", "Sample Selected"))%>%
  kable_styling()
```

@@

### Table  ###
library(kableExtra)
estimated_cost %>% 
  knitr::kable(caption = "Estimated Cost",
               col.names = c("Components", "Cost per unit", "Total cost for each component"))%>%
  kable_styling()

```
## Appendix C: Screenshot of the survey

>>>>

```{r ttest, echo=FALSE}
#install.packages("broom")
library(broom)
revenue_c <- control_data$Q13
revenue_t <- treated_data$Q13
t<-t.test(revenue_t, revenue_c)
m<-tidy(t, digits=1)
m%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    mean_of_Treated=estimate1,
    mean_of_Control=estimate2
  )%>%
  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))

@@

## Appendix A {#appendixA}
```{r AppendixA, message=FALSE,echo = FALSE}
### Number in GTA ### 
number_of_Toronto = 7500
number_of_Durham = 3260
number_of_York = 5553
number_of_Peel = 6235
number_of_Halton = 2803
number_of_GTA = sum(number_of_Toronto,number_of_Durham,number_of_York,number_of_Peel,number_of_Halton)

@@

### Table ###
library(kableExtra)
sample_size %>% 
  knitr::kable(caption = "Detailed information for stratification",
               col.names = c("Region", "Number of Restuarants", "Proportion(%)", "Sample Selected"))%>%
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

### Table  ###
library(kableExtra)
estimated_cost %>% 
  knitr::kable(caption = "Estimated Cost",
               col.names = c("Components", "Cost per unit", "Total cost for each component"))%>%
  kableExtra::kable_styling(latex_options = c("hold_position"))

\newpage
## Appendix C:
